### 2013-10-23 doc/chapters/usage.tex
add section about the configure scritp

>>>>

\subsubsection{\code{configure}}

The \code{configure} script checks for the installed compilers,
libraries and Mathematica.  If all of these exists in a sufficent
version, the \code{Makefile} is created, which contains the information
on how to compile the code.  The user has to specify the models which
should be included in the build via the \code{--with-models=} option,
e.g.
%
\begin{lstlisting}[language=bash]
./configure --with-models=<flexibsusy-model>
\end{lstlisting}
%
Here \code{<flexibsusy-model>} is either \code{all} or a comma
separated list of \flexisusy models.

Furthermore, the user can select which RG solver algorithms to use via
the \code{--with-algorithms=} option.\\
Example:
%
\begin{lstlisting}[language=bash]
./configure --with-algorithms=two_scale
\end{lstlisting}

The \code{configure} script further allows to select the C++ and
Fortran compilers, the Mathematica kernel command as well as paths to
libraries and header files.  See
\code{configure --help} for all available options.\\
Example:
%
\begin{lstlisting}[language=bash]
./configure --with-models=MSSM --with-cxx=clang++
   --with-boost-incdir=/usr/include/
   --with-boost-libdir=/usr/lib/
\end{lstlisting}
